\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-26 chapters/5_experiments_noise.tex
Update figures
Update algorithm description

\subsection{Testing the robustness of the algorithms}
 In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
 Among the update rules listed in Table \ref{tab:linkage-criteria}, we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec. \ref{sec:exp_first_comparison}. %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.

@@

    \captionof{figure}{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq. \ref{eq:opensimplex_noise_def} and c) with split-biased noise. The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar? Adapt to noise defs}}
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}

>>>>

\subsection{Different update rules and robustness to noise}
 In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
 Among the update rules listed in Table \ref{tab:linkage-criteria}, we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec. \ref{sec:exp_first_comparison}. %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.

@@

    \captionof{figure}{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq. \ref{eq:opensimplex_noise_def} and c) with split-biased noise. The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    \TODO{Add colorbar? Adapt to noise defs}}
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}
